Generative Software Development\\{\em\normalsize Research Proposal

### 2022-12-13 Generative Software/proposalBrief.tex
proposal brief made

\section{Vision}
   Generative software development uses a software generator to build information systems from a formal specification.
   Even though the idea is quite old (compilers are a form of software generator),
   this idea has not been picked up in mainstream software development.
   Yet, research so far has yielded promising results with respect to validation and resilience.
   A software generator enables the DevOps way of working, which is to demonstrate the end product at the end of every sprint.
   Thus, a way of software development emerges that allows for very fast incremental development of large information systems.
   Research at the Open Universiteit has produced software generators specifically for information systems.
   This is useful for supporting distributed business processes that require a mix of human and automated activity.

>>>>

\section{Vision}
   Generative software development uses a software generator to build information systems from a formal specification.
   Even though the idea is quite old (compilers are a form of software generator),
   this idea is not being picked up widely in the mainstream of software development.
   Yet, research so far has yielded promising results with respect to validation and resilience.
   A software generator enables the DevOps way of working, which is to demonstrate the end product at the end of every sprint.
   Thus, a way of software development emerges that allows for very fast incremental development of large information systems.
   Research at the Open Universiteit has produced software generators specifically for information systems.
   This is useful for supporting distributed business processes that require a mix of human and automated activity.
